Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-11-02 Arxiv/main.tex
update proof
revise the parameter 2 in formula into 4 and achieve \epsilon dp

\begin{definition}
\label{def_smoo_2}
$\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
  \hexpmechPr{\dataobs}{z = r} = \frac {exp\big(\frac{-\epsilon\cdot \ux{r}}{2\cdot S(\dataobs)}\big)}
{\unomalizer{\dataobs}}.
\end{equation*}
where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Theorem \ref{thm_gamma_smooth} by setting $\gamma = 1$.
\end{definition}

@@

Under this smooth sensitivity, we define $\hexpmech$ as:

\subsubsection{$\hexpmech$ $2\epsilon-$Differential Privacy Proof}

\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $2\epsilon$-differential privacy.
\end{lem}

@@

  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
  \begin{equation*}
  \hexpmechPr{\dataobs}{z = r} \leq e^{2\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
  \end{equation*}

  By definition \ref{def_smoo_2}:
  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{2\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{2\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
  \begin{equation*}
  \begin{split}
  & \leq \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon}{2} \big) \\
  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs)}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)\\
  & = exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{2}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{2} \cdot \gamma
  \big)\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  \end{split}
  \end{equation*}

  Doing the same transformation in the denominator:
  \begin{equation*}
  \begin{split}
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)}
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{2 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'})}{2\cdot S(\dataobs')}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon\cdot(\ux{r'})}{2}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{2} \geq  \frac{-\epsilon}{2}$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon}{2}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
  $\frac{- \epsilon}{2}
  (\frac{1}{S(\dataobs)}-
  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{2} \cdot \gamma$
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon}{2} \cdot \gamma
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2} +   \frac{- \epsilon}{2} \cdot \gamma
  \big)
  }\\
  & = e^{(\epsilon + \epsilon \cdot \gamma )} \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{2\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{2 \cdot S(\dataobs')}
  \big)
  }\\
  & = e^{( \epsilon + \epsilon \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
  \end{split}
  \end{equation*}

  Given $\gamma = 1$, $2\epsilon - $differential privacy can be achieved.
\end{proof}

>>>>

@@

\subsubsection{$\hexpmech$ Proposition}

\begin{definition}
\label{def_smoo_2}
$\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
  \hexpmechPr{\dataobs}{z = r} = \frac {exp\big(\frac{-\epsilon\cdot \ux{r}}{4\cdot S(\dataobs)}\big)}
{\unomalizer{\dataobs}}.
\end{equation*}
where $\ux{r} = \hellinger(\bysinfer(\dataobs),r)$ for $r \in \candidateset$ and $S(\dataobs)$ is the $\gamma -$smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated from Theorem \ref{thm_gamma_smooth} by setting $\gamma = 1$.
\end{definition}

\section{Privacy Analysis}

\subsection{Privacy Analysis for Baseline Mechanisms}
In baseline mechanisms, \emph{exponential mechanism}, \emph{Laplace mechanism}, \emph{improved Laplace mechanism} are $\epsilon-$differential privacy provided by \cite{dwork2014algorithmic}. The \emph{exponential mechanism with local sensitivity} is non-differential privacy, also from \cite{dwork2014algorithmic}.

\subsubsection{$\hexpmech$ $\epsilon-$Differential Privacy Proof}

\begin{lem}
\label{lem_hexpmech_privacy}
$\hexpmech$ is $\epsilon$-differential privacy.
\end{lem}

@@

  For any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$ and any beta distribution $r$:
  \begin{equation*}
  \hexpmechPr{\dataobs}{z = r} \leq e^{\epsilon} \hexpmechPr{\dataobs'}{z = r}. 
  \end{equation*}

  By definition \ref{def_smoo_2}:
  \begin{equation*}
  \begin{split}
  \hexpmechPr{\dataobs}{z = r} 
  & = \frac {exp\big(\frac{-\epsilon\cdot\ux{r}}{4\cdot S(\dataobs)}\big)}{\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\ux{r} + \uxadj{r} - \uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}} \\
  & = \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon\cdot(\uxadj{r} - \ux{r})}{4\cdot S(\dataobs)} \big)\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\uxadj{r} - \ux{r})$:
  \begin{equation*}
  \begin{split}
  & \leq \frac {exp\big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)}
  {\unomalizer{\dataobs}}
  \cdot exp\big( \frac{\epsilon}{4} \big) \\
  & = exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs)}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)\\
  & = exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r})}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{4}(\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)})
  \big)\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$smooth sensitivity: $\frac{1}{S(\dataobs')} - \frac{1}{S(\dataobs)} \leq \gamma$:  
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{4} \big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}
  exp
  \big(
  \frac{\epsilon}{4} \cdot \gamma
  \big)\\
  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {\unomalizer{\dataobs}}\\
  \end{split}
  \end{equation*}

  Doing the same transformation in the denominator:
  \begin{equation*}
  \begin{split}
  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} + \uxadj{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)}
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $S(\dataobs) \geq LS(\dataobs) \geq (\ux{r} - \uxadj{r})$ $\implies$ $ \frac{-\epsilon\cdot(\ux{r'} - \uxadj{r'})}{4 \cdot S(\dataobs)} \geq \frac{-\epsilon}{2}$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs)}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  exp
  \big(
  \frac{\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'})}{4\cdot S(\dataobs')}
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{2}
  \big)
  exp
  \big(
  \frac{- \epsilon\cdot(\ux{r'})}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because $\uxadj{r} = \hellinger(\bysinfer(\dataobs'), r) \leq 1$ $\implies$ $\frac{- \epsilon\cdot(\ux{r'})}{4} \geq  \frac{-\epsilon}{4}$:
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  exp
  \big(
  \frac{- \epsilon}{4}
  (\frac{1}{S(\dataobs)}
-
  \frac{1}{S(\dataobs')})
  \big)
  }\\
  \end{split}
  \end{equation*}

  Because the property of $\gamma -$ smooth sensitivity: $\frac{1}{S(\dataobs)} - \frac{1}{S(\dataobs')} \leq \gamma$ $\implies$
  $\frac{- \epsilon}{4}
  (\frac{1}{S(\dataobs)}-
  \frac{1}{S(\dataobs')}) \geq \frac{- \epsilon}{4} \cdot \gamma$
  \begin{equation*}
  \begin{split}
  & \leq exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{4}
  \big)
  exp
  \big(
  \frac{- \epsilon}{4} \cdot \gamma
  \big)
  }\\
  & = exp\big( \frac{\epsilon}{4} + \frac{\epsilon}{4} \cdot \gamma\big) \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4 \cdot S(\dataobs')}
  \big)
  exp 
  \big(
  \frac{-\epsilon}{4} +   \frac{- \epsilon}{4} \cdot \gamma
  \big)
  }\\
  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot 
  \frac {
  exp
  \big(
  \frac{-\epsilon\cdot(\uxadj{r})}{4\cdot S(\dataobs')}
  \big)
  } 
  {
  \sum_{r'\in \candidateset} 
  exp 
  \big(
  \frac{-\epsilon\cdot(\uxadj{r'}}{4\cdot S(\dataobs')}
  \big)
  }\\
  & = e^{( \frac{\epsilon}{2} + \frac{\epsilon}{2} \cdot \gamma )} \cdot   \hexpmechPr{\dataobs'}{z = r}
  \end{split}
  \end{equation*}

  Given $\gamma = 1$, $\epsilon - $differential privacy can be achieved.
\end{proof}
